%-------------------------
% Resume Template in LaTeX
% Author: Chandan Sharma
% License: MIT
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.5in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING (Centered)-----------------
\begin{center}
  \textbf{\LARGE Chandan Sharma} \\
  \vspace{0.3cm} % Space below the name
  \begin{tabular}{c c c c}
    Email: {chandansharma9008@gmail.com} &
    \hspace{1cm} % Adjust gap between items
    \href{https://www.linkedin.com/in/chandan-sharma-2807262a4/}{LinkedIn} &
    \hspace{1cm} % Adjust gap between items
    \href{https://github.com/ChandanSharma22}{GitHub} &
    \hspace{1cm} % Adjust gap between items
    Mobile: +91-9082171497 \\
  \end{tabular}
\end{center}

%-----------PROFILE-----------------
\section{Profile}
\resumeItem{}{I'm an enthusiastic and forward-thinking young man, dedicated to achieving success in my chosen field. With a readiness to explore new opportunities and embrace them with zeal, I'm prepared to develop my abilities as a supportive team member.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Nanak Khalsa College}{Matunga, Mumbai}
      {Bachelor of Science, Information Technology (GPA: 7.5/10)}{Sept 2021 -- May 2024}
      
    \resumeSubheading
      {S.I.W.S Jr College}{Wadala, Mumbai}
      {Commerce; Maharashtra Board (81\%)}{May 2019 -- Sept 2021}
  \resumeSubHeadingListEnd
  \vspace{0.5cm} % Additional space after Education section

%--------PROGRAMMING SKILLS------------
    \section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{}{ 
      \textbf{Languages}{: Python, Java, MongoDB, SQL, HTML, CSS}
    }
    \resumeSubItem{}{
      \textbf{Technologies}{: AWS, Android Studio, Visual Studio, Kali Linux, Cisco}
    }
  \resumeSubHeadingListEnd
  \vspace{0.5cm} % Additional space after Programming Skills section

  %-----------LANGUAGES-----------------
\section{Languages}
 \resumeSubHeadingListStart
    \resumeSubItem{}{ 
      \textbf{Hindi}{: Fluent}
    }
    \resumeSubItem{}{
      \textbf{English}{: Fluent}
    }
    \resumeSubItem{}{
      \textbf{Marathi}{: Fluent}
    }
  \resumeSubHeadingListEnd
 

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://github.com/ChandanSharma22/WhatsApp}{WhatsApp Clone (Android Application)}}{}{}{}
      \resumeItemListStart
        \resumeItem{Description:}
          {Developed a fully functional messaging app simulating core features of WhatsApp.}
        \resumeItem{Key Features:}
          {Implemented real-time messaging, user authentication, and profile management using Firebase Authentication and Firebase Realtime Database.}
        \resumeItem{Additional Features:}
          {Integrated multimedia sharing (images, videos) using Firebase Cloud Storage.}
        \resumeItem{Technologies Used:}
          {Java, XML, Firebase Authentication, Firebase Realtime Database, Firebase Cloud Storage, Android Studio, Git.}
      \resumeItemListEnd
      \hspace{1cm}

    \resumeSubheading
      {\href{https://github.com/ChandanSharma22/portfolio}{Portfolio Website}}{}{}{}
      \resumeItemListStart
        \resumeItem{Description:}
          {Designed and developed a personal portfolio website to showcase skills, projects, and work experience.}
        \resumeItem{Key Features:}
          {Responsive web design optimized for desktop and mobile devices, integrated with GitHub for project display.}
        \resumeItem{Additional Features:}
          {Implemented contact form with email notifications, animated sections, and smooth scrolling for enhanced user experience.}
        \resumeItem{Technologies Used:}
          {HTML, CSS, JavaScript, Bootstrap, GitHub Pages.}
      \resumeItemListEnd
      \hspace{1cm}

    \resumeSubheading
      {\href{https://github.com/ChandanSharma22/todo-app}{To-Do List App (Android Application)}}{}{}{}
      \resumeItemListStart
        \resumeItem{Description:}
          {Built a simple and intuitive to-do list app to help users manage daily tasks efficiently.}
        \resumeItem{Key Features:}
          {Added features like task creation, editing, deletion, and task completion tracking.}
        \resumeItem{Additional Features:}
          {Integrated reminder notifications for important tasks and task filtering based on priority.}
        \resumeItem{Technologies Used:}
          {Java, XML, SQLite, Android Studio.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{0.5cm} % Additional space after Projects section

%-----------CERTIFICATIONS-----------------
\section{Certifications}
 \resumeSubHeadingListStart
    \resumeSubItem{}{
      \textbf{Introduction to Cybersecurity and Digital Safety} by IQAC\hfill March 2023
    }
    \resumeSubItem{}{
      \textbf{AWS Certified Cloud Practitioner} \hfill March 2024
    }
    \resumeSubItem{}{
      \textbf{Introduction to Data Analysis using Microsoft Excel} by Coursera  \hfill July 2024
    }
  \resumeSubHeadingListEnd
  \vspace{0.5cm} % Additional space after Certifications section

%-----------EXTRACURRICULAR ACTIVITIES------------
\section{Extracurricular Activities}
 \resumeSubHeadingListStart
    \resumeSubItem{}{
      \textbf{NSS Volunteer} - National Service Scheme (2023 - 2024)
    }
    \resumeSubItem{}{
      Participated in community service activities including:
      \resumeItemListStart
        \resumeItem{Blood Donation Drives}{Organized and participated in multiple blood donation camps to support local hospitals.}
        \resumeItem{Environmental Awareness Campaigns}{Conducted tree plantation drives and cleanliness drives in local communities.}
        \resumeItem{Health Camps}{Assisted in organizing free health check-up camps for underprivileged communities.}
      \resumeItemListEnd
    }
 \resumeSubHeadingListEnd

\end{document}
